MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-30 paper.Rmd
Working on example

```{r}
library(Recca)
```

>>>>

```{r}
library(IEATools)
library(PFUSetup)
home_path <- "ExampleFolder"
iea_folder_path <- file.path(home_path, "IEA extended energy balance data")
iea_data_path <- file.path("IEA extended energy balance data", "GH-ZA-TJ-Extended-Energy-Balances-sample-2022.csv")
setup <- PFUSetup::get_abs_paths(home_path = file.path("ExampleFolder"), 
                                 dropbox_path = "",
                                 project_path = "",
                                 iea_folder_path = iea_folder_path,
                                 iea_data_path = iea_data_path,
                                 version = "v_example")
```
